Characteristics of Top Songs Has Changed from Pandemic Brain

### 2024-04-19 paper/paper.qmd
Fixed causal model in paper and fixed formatting

### Model justification
```{r}
#| label: fig-causal-model
#| fig-cap: Causal relationship between song characteristics and hit song (before 2020 or during and after 2020)
#| echo: false
#| warning: false
#| message: false

# Referenced https://www.erikigelstrom.com/articles/causal-graphs-in-r-with-diagrammer/ and https://stackoverflow.com/questions/42737645/how-to-export-images-of-diagrammer-in-r for code
causal_model <- "digraph {
  graph []
  # Nodes
  node [shape = plaintext]
    A [label = 'Hit song before 2020 or during and after 2020']
    B [label = 'Modality']
    C [label = 'Loudness']
    D [label = 'Duration']
    E [label = 'Tempo']
    F [label = 'Lyrics (Confounder)']
  # Edges for non-confounding variables
  edge []
    B->A
    C->A
    D->A
    E->A
{ rank = same; }
  # Edges for confounding variable
  edge [style = dashed]
    F -> B
    F -> C
    F -> D
    F -> E
    F -> A
}"
# Export the drawing as a png
exporting_image <- grViz(causal_model) |>
  export_svg() |>
  charToRaw() |>
  rsvg_png("../other/sketches/graph_2_casual_model.png", width = 1000)

>>>>

## Model justification
```{r}
#| label: fig-causal-model
#| fig-cap: Causal relationship between song characteristics and hit song before 2020
#| echo: false
#| warning: false
#| message: false

# Referenced https://www.erikigelstrom.com/articles/causal-graphs-in-r-with-diagrammer/ and https://stackoverflow.com/questions/42737645/how-to-export-images-of-diagrammer-in-r for code
causal_model <- "digraph {
  graph []
  # Nodes
  node [shape = plaintext]
    A [label = 'Hit song before 2020']
    B [label = 'Modality']
    C [label = 'Loudness']
    D [label = 'Duration']
    E [label = 'Tempo']
    F [label = 'Lyrics (Confounder)']
  # Edges for non-confounding variables
  edge []
    B->A
    C->A
    D->A
    E->A
{ rank = same; }
  # Edges for confounding variable
  edge [style = dashed]
    F -> B
    F -> C
    F -> D
    F -> E
    F -> A
}"
# Export the drawing as a png
exporting_image <- grViz(causal_model) |>
  export_svg() |>
  charToRaw() |>
  rsvg_png("../other/sketches/graph_2_casual_model.png", width = 1000)
